### 2020-03-26 HICSSSubmission/bp_studyMethod.tex
moved related work to the end, still need to cut 3 pages

\subsection{Participants}
We recruited group of 14 professionals via personal contacts from a large power and automation company. The group is diverse in terms of age, work experience, gender, and work responsibilities. All participants work primarily in an office environment, though half of the participants spend at least 10\% (and up to 50\%) of their time in a laboratory environment. Office workers are a population that generalizes to a variety of contexts, and including part-time laboratory workers guarantees that our participants have varying work patterns that include different levels of computer usage, as well as different levels of activity in both individual and collaborative tasks.

@@

\subsubsection{Biometric Sensors}
Figure~\ref{everion} illustrates Biovotion's Everion, which we used to track the biometric signals of the study participants. The Everion is worn on the upper arm and provides continuous monitoring of certain biometric measurements.\footnote{https://biovotion.zendesk.com/hc/en-us/categories/201633909-Everion-Device} Previous studies~\cite{zuger18,sano2013stress,healey2005detecting,wijsman2011towards,zuger2015interruptibility,goyal2017intelligent} have used similar devices~\cite{Okada11,polar,fitbitCharge} to capture psycho-physiological and biometric measurements for shorter periods of time or capturing a smaller number of measurements.

>>>>

\subsection{Participants}
We recruited a group of 14 professionals via personal contacts from a large power and automation company. The group is diverse in terms of age, work experience, gender, and work responsibilities. All participants work primarily in an office environment, though half of the participants spend at least 10\% (and up to 50\%) of their time in a laboratory environment. Office workers are a population that generalizes to a variety of contexts, and including part-time laboratory workers guarantees that our participants have varying work patterns that include different levels of computer usage, as well as different levels of activity in both individual and collaborative tasks.

@@

\subsubsection{Biometric Sensors}
Figure~\ref{everion} illustrates Biovotion's Everion, which we used to track the biometric signals of the study participants. The Everion is worn on the upper arm and provides continuous monitoring of certain biometric measurements.\footnote{https://biovotion.zendesk.com/hc/en-us/articles/213613165} Previous studies~\cite{zuger18,sano2013stress,healey2005detecting,wijsman2011towards,zuger2015interruptibility,goyal2017intelligent} have used similar devices~\cite{Okada11,polar,fitbitCharge} to capture psycho-physiological and biometric measurements for shorter periods of time or capturing a smaller number of measurements.
